Backpropagating Gravitational wave events

### 2022-03-14 src/ms.tex
Add figures

We show our main result in figure \ref{fig:GW150914_posterior}. 
\kw{Recover ratio of the posterior sample goes here.}

@@

\kw{Add figure of stable mass transfer vs common envelope}

>>>>

We show a portion of the joint posterior of the progenitor parameters and hyper-parameters of GW150914 in figure \ref{fig:GW150914_posterior}.
\kw{Recover ratio of the posterior sample goes here.}

The full posterior is available in appendix \kw{Or we should w=put a link to the dataset?}

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GW150914_CE_SMT.pdf}
\caption{}
\label{fig:GW150914_CE_SMT}
\end{figure}
\kw{Add figure of stable mass transfer vs common envelope}

\begin{figure}
\caption{}
\label{fig:GW150914_M1_M2_q3}
\end{figure}

The most important point in this paper is illustrated in figure \ref{fig:GW150914_M1_M2_q3}.
We can see the posterior samples in $M_1-M_2$ space are spatially correlated with $q_3$,
this means if we fixed the value of $q_3$ instead of allowing it to jointly vary with all other parameters,
we would miss the samples that do not match the fixed value of $q_3$.
Comparing our result with 
\kw{Add figure showing hyper-parameters are important to recovering the progenitor parameters incorrectly.}
